An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
add acknowledgement

\begin{algorithm}[h]
 \SetKwFor{For}{for}{}{end}
 \SetKwFor{While}{while}{}{end}
 \SetKwFor{If}{if}{}{end}
 \SetKwFunction{nei}{forward-neighbors}
 \SetKwFunction{enqueue}{enqueue}
 \SetKwFunction{nz}{nonzeros}
 \SetKwFunction{intersect}{intersect}
 \SetKwFunction{map}{map}
 \SetKwProg{Fn}{function}{}{end}
 \Fn{ABFS($A_n, (s,t)$)}{
   Form $\bm{A}^T$ from $A_n$\\
   $m = A^{[1]}.dimension$ \\
   $b$ is a sparse vector of length $mn$ \\
   $b(s+mt) =1$ \\
   $i = 1$ \\
   $dict.(s,t) = 0$ \\
   \While{\nz{$b$} $\ne \emptyset$}{
       $\bm{b} = \bm{A}^T\bm{b}$ \\
       \For{$i$ in \nz{$b$}}{
         $node =$ \map{$i$} \\
         \If{$node$ in $dict$}{
           $b(i) = 0$ \\
         }
      }
      $nodes =$\map{$b$}\\
       \For{$node$ in $nodes$}{
           $dict.node = i$
         }

@@

Algorithm \ref{alg:bfsla} outlines the basic idea of an algebraic evolving-graph BFS.
But in practice we don't need to form $\bm{A}$ and $\bm{b}$ explicitly at step $4$ and $6$. By realizing the dependency between these sparse matrices,
we can compute  the result in parallel.

@@

% % use section* for acknowledgement
% \section*{Acknowledgment}

% The authors would like to thank...
% more thanks here

>>>>

\begin{algorithm}[h]
 \SetKwFor{For}{for}{}{end}
 \SetKwFor{While}{while}{}{end}
 \SetKwFor{If}{if}{}{end}
 \SetKwFunction{nei}{forward-neighbors}
 \SetKwFunction{enqueue}{enqueue}
 \SetKwFunction{nz}{nonzeros}
 \SetKwFunction{intersect}{intersect}
 \SetKwFunction{map}{map}
 \SetKwProg{Fn}{function}{}{end}
 \Fn{ABFS($A_n, (s,t)$)}{
   Form $\bm{A}^T$ from $A_n$.\\
   Let $m$ be the dimension of  $A^{[1]}$. \\
   $b$ is a sparse vector of length $mn$ \\
   $b(s+mt) =1$ \\
   $i = 1$ \\
   $dict.(s,t) = 0$ \\
   \While{\nz{$b$} $\ne \emptyset$}{
       $\bm{b} = \bm{A}^T\bm{b}$ \\
       \For{$i$ in \nz{$b$}}{
         $node =$ \map{$i$} \\
         \If{$node$ in $dict$}{
           $b(i) = 0$ \\
         }
      }
      $nodes =$\map{$b$}\\
       \For{$node$ in $nodes$}{
           $dict.node = i$
         }

@@

Algorithm \ref{alg:bfsla} outlines the basic idea of an algebraic evolving-graph BFS.
But in practice we don't need to form $\bm{A}$ explicitly at step $2$. By realizing the dependency between these sparse matrices,
we can compute  the result in parallel.

@@

\section*{Acknowledgment}

The authors are grateful to Professor Nicholas J. Higham and Doctor Vedran \u Sego for suggestions.
This work was completed while the second author visited MIT CSAIL. He thanks 
Professor Alan Edelman for making his stay so pleasant.
